### 2008-12-17 talk/ecoop2009/benchmarks.tex
add high level syntax of two benchmarks.

The benchmarks have been run on machine XXX with hardware YYY etc. etc.

@@

To benchmark arithmetic operations between integers, we wrote a simple program
that computes the factorial of a given number.  The algorithm is
straightforward, and the loop contains only three operations: one
multiplication, one subtraction, and one comparison to check if we have
finished the job.

@@

Moreover, we also wrote a program to calculate the $n_{th}$ Fibonacci number,
for which we can do the same reasoning as above.

@@

\anto{Should we say that we get wrong results due to overflow but we don't care?}

>>>>

The benchmarks have been run on machine with Intel Pentium 4 CPU running at
3.20 GHz and 2 GB of RAM, running Microsoft Windows XP and Microsoft .NET
Framework 2.0.

@@

To benchmark arithmetic operations between integers, we wrote a simple program
that computes the factorial of a given number.  The algorithm is
straightforward, and the loop contains only three operations: one
multiplication, one subtraction, and one comparison to check if we have
finished the job:

\begin{lstlisting}
def main(n):
    result = 1
    while n > 1:
        result = result * n
        n = n - 1
    return n
\end{lstlisting}

@@

Similarly, we wrote a program to calculate the $n_{th}$ Fibonacci number, for
which we can do the same reasoning as above:

\begin{lstlisting}
def main(n):
    a = 0
    b = 1
    while n > 1:
        sum = a + b
        a = b
        b = sum
        n = n - 1
    return b
\end{lstlisting}

@@

Note that do get meaningful timings, we had to calculate the factorial and
Fibonacci of very high numbers.  This means that the results are incorrect due
to overflow, but since all the runnings overflows in the very same way, the
timings are still comparable. \anto{I think we should rephrase this sentence}.
